Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-09 draft.tex
minor changes

The diagram above is model-independent,
but we will check that the analogous diagram~\eqref{eq:comdiagforcentralizercomput} commutes when we use our models $\bU_n \fg$, $\bZ_n(f)$, and so on for the objects and when we use our factorization maps $\ev_{{\bf f}}$ (for $\ev_f$), ${\bf 1}$ (for the unit elements $1$),  and so on.
In particular, we use $(-\star-)$ for~$\Upsilon$.

@@

Next, recall that to an open set $U \subset M$ the factorization algebra ${\rm Gr} \; \bZ_n (\fg)$ assigns the cochain complex whose underlying 
\[
\clie^\bu\bigg(\fg \otimes \Omega^\bu (U) \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c(U) [1]\right) \bigg) = {\rm Hom}^\bu \bigg(\cliels(\fg \otimes \Omega^\bu(U)) , \cliels (\fg \otimes \Omega^\bu_c(U)) \bigg).
\]
\brian{how to handle homs}.
\end{proof}

@@

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
\]
\end{itemize}
The structure map associated to the embedding 
\begin{equation}\label{eqn:embed}
U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\end{equation}
is given by the composition
\[
\begin{tikzcd}
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V\times [0,\epsilon)) [2] \right) \ar[d] \\
\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d] \\
\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d]\\
\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
\end{tikzcd}
\]
The first map evaluates the unit in $\Sym\left(\fg \otimes \Omega^\bu(U)\right)$ and the second map uses the fact that the symmetric algebra functor is monoidal. 
Finally, the third map is induced by the extension of compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 
\end{dfn}

@@

\begin{proof}
Note that as an underlying graded vector space $\Tilde{\bZ}_n(\fg) (U)$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (U)[1]) \; , \; {\rm Sym}  \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \right)  .
\]
\brian{explain notation with homs} 
Let $x^* \otimes \alpha$ denote an element of $\fg \otimes \Bar{\Omega}_c (U)$ and $y \otimes \beta$ denote an element of $\fg \otimes \Omega_c(U) [2]$. 
Then, the bracket involving the linear elements $(x^* \otimes \alpha) \otimes 1$ 
and $1 \otimes (y \otimes \beta)$ is defined by
\begin{align*}
\{(x^* \otimes \alpha) \otimes 1 , 1 \otimes (y \otimes \beta)\} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
\{(x^* \otimes \alpha) \otimes 1 , (x'^* \otimes \alpha') \otimes 1\} & = 0 \\
\{1 \otimes (y \otimes \beta) , 1 \otimes (y' \otimes \beta')\} & = 0 . 
\end{align*}
Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. 
The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.
\end{proof}

>>>>

The diagram above is model-independent,
but we will check that the analogous diagram~\eqref{eq:comdiagforcentralizercomput} commutes when we use our models $\bU_n (\fg)$, $\bZ_n(f)$, and so on for the objects and when we use our factorization maps $\ev_{{\bf f}}$ (for $\ev_f$), ${\bf 1}$ (for the unit elements $1$),  and so on.
In particular, we use $(-\star-)$ for~$\Upsilon$.

@@

Next, recall that to an open set $U \subset M$ the factorization algebra ${\rm Gr} \; \bZ_n (\fg)$ assigns the cochain complex
\[
\clie^\bu\bigg(\fg \otimes \Omega^\bu (U) \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c(U) [1]\right) \bigg) = {\rm Hom}^\bu \bigg(\cliels(\fg \otimes \Omega^\bu(U)) , \cliels (\fg \otimes \Omega^\bu_c(U)) \bigg).
\]
\brian{how to handle homs}.
\end{proof}

@@

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
\]
\end{itemize}
The structure map associated to the embedding 
\begin{equation}\label{eqn:embed}
i : U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\end{equation}
is given by the composition
\[
\begin{tikzcd}
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V\times [0,\epsilon)) [2] \right) \ar[d, "{\rm ev}_1"] \\
\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d, "\simeq"] \\
\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d, "i_*"]\\
\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
\end{tikzcd}
\]
The first map ${\rm ev}_1$ evaluates the unit $1$ in $\Sym\left(\fg \otimes \Omega^\bu(U)\right)$ and the second map uses the fact that the symmetric algebra functor is monoidal. 
Finally, the third map is induced by the extension of compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 
\end{dfn}

@@

\begin{proof}
For $U \subset M \times \RR_{>0}$ the underlying graded vector space of $\bC_n(\fg)(U)$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (U)[1]) \; , \; {\rm Sym}  \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \right)  .
\]
Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U) \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [2]$. 
Then, the bracket involving the linear elements $x^* \otimes \alpha$ 
and $y \otimes \beta$ is defined by
\begin{align*}
\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
\end{align*}
Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. \brian{how to say this now}
The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.
\end{proof}
